---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(tidytext)
library(lubridate)
library(ggthemes)
```


```{r}
df <- read_csv("~/downloads/reddit_coffee_submissions.csv")
```




```{r}
# create date

df <- df %>% mutate(dt = as.Date(created_date))
```


```{r}
custom_stop_words <- tibble(word = c("na", "drink", "cocktail", "recipe", "shake", "ice", "1", "2", "oz", "ounces", "http","https", "cocktails", "recipes", "amp", "4", "favorite", "love",
                                     "removed", "imgur", "i.imgur", "NA", "keywords", "na", "utf8", "amp", "qid", "sr"))
```


```{r}
df <- df %>% mutate(combined_text = paste0(title," ", text))
```

```{r}
tokenized_df <- df %>%
  select(post_id, combined_text, dt, score, numcomms) %>% 
  unnest_tokens(word, combined_text)

tokenized_df <- tokenized_df %>% 
  anti_join(stop_words) %>% 
  anti_join(custom_stop_words)


bigram_df <- df %>% 
  select(post_id, combined_text, dt, score, numcomms) %>% 
  unnest_tokens(bigram, combined_text, "ngrams",  n = 2)
```


posts per year
```{r}
post_per_year <- df %>% count(year = year(dt)) %>% rename(yearly_posts = n)
```

Number of posts seems to have gone down quite a bit

```{r}
post_per_year %>%
  ggplot(aes(x = year, y = yearly_posts)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
tokenized_df %>% 
  count(word, year = year(dt), sort = T) %>% 
  filter(n > 2000) %>% 
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_col() +
  coord_flip() +
  facet_wrap(~year, scales = "free")
```

# Visualizing bigrams
```{r}
library(ggplot2)
library(igraph)
library(ggraph)

count_bigrams <- function(dataset) {
  dataset %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(!word1 %in% stop_words$word,
           !word2 %in% stop_words$word,
           !word1 %in% custom_stop_words$word,
           !word2 %in% custom_stop_words$word) %>%
    count(word1, word2, sort = TRUE)
}

visualize_bigrams <- function(bigrams, min_number = 600) {
  set.seed(2016)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    filter(n > min_number) %>% 
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void()
}
```


```{r}
bg <- count_bigrams(df)


# play with min_number until chart is as dense as you want it to be
bg %>%
  filter(!is.na(word1),
         !is.na(word2)) %>% 
  visualize_bigrams(min_number = 350)
```

```{r}
word_over_time_month <- function(ingredient){
  tokenized_df %>%
    mutate(month = as.Date(cut(tokenized_df$dt, breaks = "month"))) %>% 
    distinct() %>% 
    filter(word == ingredient) %>% 
    count(month) %>% 
    ggplot(aes(x = month, y = n)) +
    geom_col()
}

word_over_time_year <- function(ingredient){
  tokenized_df %>%
    mutate(year = year(dt)) %>% 
    filter(word == ingredient) %>% 
    distinct() %>% 
    count(year) %>% 
    inner_join(post_per_year) %>% 
    mutate(posts_per_thousand = 1000 * n / yearly_posts)
}


bigram_year <- function(two_words){
  bigram_df %>%
    mutate(year = year(dt)) %>% 
    filter(bigram == two_words) %>% 
    distinct() %>% 
    count(year) %>% 
    inner_join(post_per_year) %>% 
    mutate(posts_per_thousand = 1000 * n / yearly_posts)
}

```

Setting a hex color for plotting
```{r}
coffee <- "#693d26"
```


# cold brew

```{r}
bigram_year("cold brew") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019))
```


```{r}
bigram_year("iced coffee") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019))
```


# iced coffee vs cold brew

```{r}
coldbrew <- bigram_year("cold brew") %>%
  mutate(term = "cold brew")

iced_coffee <- bigram_year("iced coffee") %>% 
  mutate(term = "iced coffee")

cold <- coldbrew %>%
  rbind(iced_coffee)

cold %>% 
  ggplot(aes(x = year, y = posts_per_thousand, group = term)) +
  geom_line(aes(color = term)) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold")
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'French Press' \non Reddit's Coffee Forum")
```

```{r}
scale_fill_discrete(c(coffee, "#f0cf8d"))

cold %>% 
  ggplot(aes(x = year, y = posts_per_thousand, group = term)) +
  geom_col(aes(fill = term)) +
  scale_fill_manual(values = c(coffee, "#f0cf8d")) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Cold Brew' and\n'Iced Coffee' on Reddit's Coffee Forum")
```

```{r}
bigram_year("almond milk") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
      theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Almond Milk' \non Reddit's Coffee Forum")
  ```


```{r}
bigram_year("oat milk") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
    theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Oat Milk' \non Reddit's Coffee Forum")

```
```{r}
bigram_year("coconut milk") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Coconut Milk' \non Reddit's Coffee Forum")
```
# milk types

different function to include the word "whole" because it is in stop words dictionary
```{r}
count_bigrams_milk <- function(dataset) {
  dataset %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(#!word1 %in% stop_words$word,
           !word2 %in% stop_words$word,
           !word1 %in% custom_stop_words$word,
           !word2 %in% custom_stop_words$word) %>%
    count(word1, word2, sort = TRUE)
}

```


```{r}
milk_counts <- df %>% 
  filter(dt > '2018-01-01') %>% 
  count_bigrams_milk() %>% 
  filter(word2 == "milk") %>% 
  arrange(-n)
```

```{r}
milk_words <- c("regular", "whole", "skim", "cow", "cow's", "cashew", "nut", "almond", "oat", "soy", "goat", "macadamia", "plant", "raw", "condensed", "chocolate")

milk_counts$word1 <- gsub("cow's", "cow", milk_counts$word1)

milk_counts <- milk_counts %>%
  group_by(word1) %>% 
  summarise(n = sum(n)) %>% 
  arrange(-n)

milk_counts %>% 
  filter(word1 %in% milk_words) %>% 
  ggplot(aes(x = reorder(word1, n), y = n)) +
  geom_col(fill = coffee) +
  coord_flip() +
  theme_wsj() +
  labs(x = "Milk Type", y = "Mentions per Thousand Posts", title = "Most commonly mentioned\nmilk types on Reddit's coffee forum",
       caption = "2018-2019")
```

#styles

```{r}
word_over_time_year("espresso") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Espresso' \non Reddit's Coffee Forum")
```

Cappuccino

```{r}
word_over_time_year("cappuccino") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Cappuccino' \non Reddit's Coffee Forum")
```


```{r}
word_over_time_year("latte") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Latte' \non Reddit's Coffee Forum")
```

Cortado

```{r}
word_over_time_year("cortado") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Cortado' \non Reddit's Coffee Forum")
```

# machiatto

```{r}
word_over_time_year("macchiato") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Macchiato' \non Reddit's Coffee Forum")
```


```{r}
word_over_time_year("ristretto") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Ristretto' \non Reddit's Coffee Forum")
```



```{r}
word_over_time_year("americano") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Americano' \non Reddit's Coffee Forum")
```

```{r}
word_over_time_year("affogato") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Affogato' \non Reddit's Coffee Forum")
```

```{r}
bigram_year("flat white") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Flat White' \non Reddit's Coffee Forum")

```


```{r}
word_over_time_year("mocha") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Mocha' \non Reddit's Coffee Forum")
```
# methods

```{r}
bigram_year("pour over") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Pour Over' \non Reddit's Coffee Forum")
```


```{r}
bigram_year("turkish coffee") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Turkish Coffee' \non Reddit's Coffee Forum")
```

drip
```{r}
word_over_time_year("drip") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Drip' \non Reddit's Coffee Forum")
```


Cold brew

```{r}
bigram_year("cold brew") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Cold Brew'\non Reddit's Coffee Forum")
```

```{r}
bigram_year("french press") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'French Press' \non Reddit's Coffee Forum")
```
```{r}
word_over_time_year("siphon") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Siphon' \non Reddit's Coffee Forum")
```

```{r}
word_over_time_year("percolator") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Percolator' \non Reddit's Coffee Forum")
```


```{r}
bigram_year("moka pot") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Moka Pot' \non Reddit's Coffee Forum")
```

Manual grinder
```{r}
bigram_year("manual grinder") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Manual Grinder' \non Reddit's Coffee Forum")
```

```{r}
bigram_year("burr grinder") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Burr Grinder' \non Reddit's Coffee Forum")
```


# grinds

```{r}
bigram_year("coarse grind") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Coarse Grind' \non Reddit's Coffee Forum")
```

```{r}
bigram_year("fine grind") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Fine Grind' \non Reddit's Coffee Forum")
```

# roasts
```{r}
bigram_year("dark roast") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Dark Roast' \non Reddit's Coffee Forum")
```

```{r}
bigram_year("light roast") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Light Roast' \non Reddit's Coffee Forum")
```


```{r}
bigram_year("medium roast") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +

  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Medium Roast' \non Reddit's Coffee Forum")
```

```{r}
word_over_time_year("roast") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Roast' \non Reddit's Coffee Forum")
```


# roast generally

```{r}
bg %>% filter(word2 == "roast",
              n > 500) %>% 
  ggplot(aes(x = reorder(word1, n), y= n)) +
  geom_col(aes(fill = word1)) +
  scale_fill_manual(values = c(coffee, "#f0cf8d", "#925F01")) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "none"
  ) +
  coord_flip() +
  labs(x = "", y = "Mentions", title = "Most-mentioned roasts on \nReddit's Coffee Forum")
```





# branded methods
```{r}
word_over_time_year("toddy") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Toddy' \non Reddit's Coffee Forum")
```
#aeropress

```{r}
word_over_time_year("aeropress") %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Aeropress' \non Reddit's Coffee Forum")
```



#Percolator

```{r}
word_over_time_year("percolator") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Percolator' \non Reddit's Coffee Forum")
```

#Chemex

```{r}
word_over_time_year("chemex") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Chemex' \non Reddit's Coffee Forum")
```

```{r}
word_over_time_year("bodum") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019)) +
    theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Bodum' \non Reddit's Coffee Forum")
```



```{r}
word_over_time_year("bialetti") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Bialetti' \non Reddit's Coffee Forum")
```
Interesting
High end

```{r}
word_over_time_year("hario") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
    theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Hario' \non Reddit's Coffee Forum")
```

```{r}
word_over_time_year("gaggia") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
    theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Gaggia' \non Reddit's Coffee Forum")
```


Interesting to compare to broader market /google trends --> moving mass market

```{r}
bigram_year("blue bottle") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = coffee) +
  theme_wsj() +
  theme(
    axis.title = element_text(),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.title.x = element_text(size = 11, face = "bold")
  ) +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Blue Bottle' \non Reddit's Coffee Forum", subtitel = "per thousand posts")
```



```{r}
word_over_time_year("burr") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```
```{r}
word_over_time_year("blade") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("gooseneck") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```
kalita wave
```{r}
bigram_year("kalita wave") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```
What's a steam wand
```{r}
bigram_year("steam wand") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

Buy buy buy!
```{r}
bigram_year("manual grinder") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
bigram_year("paper filter") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
bigram_year("light roast") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
bigram_year("dark roast") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
bigram_year("medium roast") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
library(ggplot2)
library(igraph)
library(ggraph)

count_bigrams <- function(dataset) {
  dataset %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(!word1 %in% stop_words$word,
           !word2 %in% stop_words$word,
           !word1 %in% custom_stop_words$word,
           !word2 %in% custom_stop_words$word) %>%
    count(word1, word2, sort = TRUE)
}

visualize_bigrams <- function(bigrams) {
  set.seed(2016)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    filter(n > 450) %>% 
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void()
}
```
Show this first

```{r}
bg <- count_bigrams(df)

bg %>%
  filter(!is.na(word1),
         !is.na(word2)) %>% 
  visualize_bigrams()
```



```{r}
df %>%
    mutate(month = as.Date(cut(df$dt, breaks = "month"))) %>% 
    count(month) %>% 
    ggplot(aes(x = month, y = n)) +
    geom_col()
```
```{r}
word_over_time_year <- function(ingredient){
  tokenized_df %>%
    mutate(yr = as.Date(cut(tokenized_df$dt, breaks = "year"))) %>% 
    filter(word == ingredient) %>% 
    distinct() %>% 
    count(yr) %>% 
    inner_join(posts_per_year) %>% 
    mutate(count_per_thousand_posts = (1000 * n / n_posts_per_year))
}
```


```{r}
word_over_time_year("sperry") %>% 
  ggplot(aes(x = yr, y = count_per_thousand_posts)) +
  geom_col(fill = "navy") +
  theme_minimal() +
  labs(x = "year", y = "mentions per thousand posts", title = "Mentions of Sperry on r/MaleFashionAdvice")
```
```{r}
word_over_time_year("bonobos") %>% 
  ggplot(aes(x = yr, y = count_per_thousand_posts)) +
  geom_col() +
  theme_minimal()
```
```{r}
word_over_time_year("converse") %>% 
  ggplot(aes(x = yr, y = count_per_thousand_posts)) +
  geom_col() +
  theme_minimal()
```

```{r}
word_over_time_year("vest") %>% 
  ggplot(aes(x = yr, y = count_per_thousand_posts)) +
  geom_col() +
  theme_minimal()
```

```{r}
word_over_time_year("sweater") %>% 
  ggplot(aes(x = yr, y = count_per_thousand_posts)) +
  geom_col() +
  theme_minimal()
```

```{r}
word_over_time_year("sperry")
```
Seems like 2017 there's an issue

```{r}
word_over_time_year("jeans") %>% 
  ggplot(aes(x = yr, y = count_per_thousand_posts)) +
  geom_col() +
  theme_minimal()
```



```{r}
word_over_time_year("shorts") %>% 
  ggplot(aes(x = yr, y = count_per_thousand_posts)) +
  geom_col() +
  theme_minimal()
```


Monthly posts to nutrition
```{r}
tokenized_df %>%
  filter(dt < as.Date('2019-01-01')) %>% 
    mutate(mth = month(dt)) %>% 
  filter(word == "fat") %>% 
    distinct() %>% 
    count(mth) %>% 
    ggplot(aes(x = mth, y = n)) +
    geom_col()
```

