---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(tidytext)
library(lubridate)
library(ggrepel)
library(ggthemes)
```


Raw data, email joe at residualthoughts dot com if you'd like me to share it with you; otherwise you can pull reddit data through the python api

```{r}
df <- read_csv("~/downloads/reddit_nutrition_submissions.csv")
```

```{r}
# create date

df <- df %>% mutate(dt = as.Date(created_date))
```

Custom stop words filter out some words we don't want to analyse that appear often in reddit text (imgur.com, for example)

```{r}
custom_stop_words <- tibble(word = c("na", "drink", "cocktail", "recipe", "shake", "ice", "1", "2", "oz", "ounces", "http","https", "cocktails", "recipes", "amp", "4", "favorite", "love", "removed", "imgur", "i.imgur", "NA", "keywords", "na", "utf8", "amp", "qid", "sr"))
```


Creating a combined text column with both heading and body text
```{r}
df <- df %>% mutate(combined_text = paste0(title," ", text))
```


Tokenizing datasets
```{r}
tokenized_df <- df %>%
  select(post_id, combined_text, dt, score, numcomms) %>% 
  unnest_tokens(word, combined_text)

tokenized_df <- tokenized_df %>% 
  anti_join(stop_words) %>% 
  anti_join(custom_stop_words)


bigram_df <- df %>% 
  select(post_id, combined_text, dt, score, numcomms) %>% 
  unnest_tokens(bigram, combined_text, "ngrams",  n = 2)
```
posts per year
```{r}
post_per_year <- df %>% count(year = year(dt)) %>% rename(yearly_posts = n)
```


# Visualizing bigrams
```{r}
library(ggplot2)
library(igraph)
library(ggraph)

count_bigrams <- function(dataset) {
  dataset %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(!word1 %in% stop_words$word,
           !word2 %in% stop_words$word,
           !word1 %in% custom_stop_words$word,
           !word2 %in% custom_stop_words$word) %>%
    count(word1, word2, sort = TRUE)
}

visualize_bigrams <- function(bigrams, min_number = 200) {
  set.seed(2016)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    filter(n > min_number) %>% 
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void()
}
```


```{r}
bg <- count_bigrams(df)

bg %>%
  filter(!is.na(word1),
         !is.na(word2)) %>% 
  visualize_bigrams()
```


# visualize only recent bigrams
Showing bigram chart for 2018 and 2019 to see newer trends

```{r}
bg_recent <- df %>% 
  filter(year(dt) == 2019 |
           year(dt) == 2018) %>% 
  count_bigrams()

bg_recent %>%
  filter(!is.na(word1),
         !is.na(word2)) %>% 
  visualize_bigrams(min_number = 100)
```

See the most commonly used words by year. For nutrition, this isn't very insightful, as the top words are mostly the same each year

```{r}
tokenized_df %>% 
  count(word, year = year(dt), sort = T) %>% 
  filter(n > 1400) %>% 
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_col() +
  coord_flip() +
  facet_wrap(~year, scales = "free")
```

Here, I'm going to look at the words with the most growth from 2018 to 2019.

```{r}
# combining bigrams and single words
bigram_and_word <- bigram_df %>%
  rename(word = bigram) %>% 
  rbind(tokenized_df) %>% 
  rename(token = word)

# only recent posts to shrink it
bigram_and_word <- bigram_and_word %>% 
  filter(dt > '2017-12-31')

# getting top words from each 
counts_2018 <- bigram_and_word %>% 
  filter(year(dt) == 2018) %>% 
  count(token, year = year(dt), sort = T) %>% 
  filter(n > 100) %>% 
  inner_join(post_per_year) %>% 
  mutate(post_per_thousand_2018 = 1000* n / yearly_posts)


counts_2019 <- bigram_and_word %>% 
  filter(year(dt) == 2019) %>% 
  count(token, year = year(dt), sort = T) %>% 
  filter(n > 50) %>% 
  inner_join(post_per_year) %>% 
  mutate(post_per_thousand_2019 = 1000* n / yearly_posts)

diff <- counts_2018 %>% 
  inner_join(counts_2019, by = c("token" = "token"))

diff <- diff %>%
  mutate(difference = post_per_thousand_2019 - post_per_thousand_2018) %>% 
  select(token, difference) %>% 
  arrange(-difference)
```



# Functions to plot trends over time

```{r}
word_over_time_month <- function(ingredient){
  tokenized_df %>%
    mutate(month = as.Date(cut(tokenized_df$dt, breaks = "month"))) %>% 
    distinct() %>% 
    filter(word == ingredient) %>% 
    count(month) %>% 
    ggplot(aes(x = month, y = n)) +
    geom_col()
}

word_over_time_year <- function(ingredient){
  tokenized_df %>%
    mutate(year = year(dt)) %>% 
    filter(word == ingredient) %>% 
    distinct() %>% 
    count(year) %>% 
    inner_join(post_per_year) %>% 
    mutate(posts_per_thousand = 1000 * n / yearly_posts)
}


bigram_year <- function(two_words){
  bigram_df %>%
    mutate(year = year(dt)) %>% 
    filter(bigram == two_words) %>% 
    distinct() %>% 
    count(year) %>% 
    inner_join(post_per_year) %>% 
    mutate(posts_per_thousand = 1000 * n / yearly_posts)
}

```

# Greek yogurt
```{r}
bigram_year("greek yogurt") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019)) +
  theme_minimal() +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Greek Yogurt Mentions on Reddit's Nutrition Forum")
```

```{r}
bigram_year("plant based") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019)) +
  theme_minimal() +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Plant Based' on Reddit's Nutrition Forum")
```
```{r}
word_over_time_year("potassium") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy")
```

```{r}
bigram_year("amino acids") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
bigram_year("healthy fats") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```


```{r}
bigram_year("green smoothie") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy")
```
```{r}
bigram_year("high protein") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy")
```


```{r}
word_over_time_year("chobani") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("avocado") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
avocado <- read_csv("~/Downloads/avo_trends.csv")

avocado_yearly <- avocado %>% 
  group_by(Month) %>% 
  summarise(yearly_google_index = mean(avocado)) %>% 
  rename(year = Month)   # i had accidentally named the date month when importing google sheet
```


Have to create dataset for labels, this is an annoying step
```{r}
index_label_data <- word_over_time_year("avocado") %>% 
  inner_join(avocado_yearly, by = c("year" = "year")) %>% 
  mutate(reddit_index = posts_per_thousand / 3.021148,
         google_index = yearly_google_index / 31.9167) %>%
  select(year, reddit_index, google_index) %>% 
  gather(key = "type", value = "index", 2:3) %>%   # have to reshape data to plot them together on one chart
  arrange(year) %>% 
  filter(year == 2017)
```



```{r}
word_over_time_year("avocado") %>% 
  inner_join(avocado_yearly, by = c("year" = "year")) %>% 
  mutate(reddit_index = posts_per_thousand / 3.021148,
         google_index = yearly_google_index / 31.9167) %>%
  select(year, reddit_index, google_index) %>% 
  gather(key = "type", value = "index", 2:3) %>%   # have to reshape data to plot them together on one chart
  arrange(year) %>% 
  ggplot(aes(x = year, y = index, group = type)) +
  geom_line(aes(color = type), size = 1) +
  geom_text(data = index_label_data, aes(label = type, vjust = -2)) +
  scale_x_continuous(breaks = c(2010:2019)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(x = "", y = "index", title = "Avocados on Google and Reddit")
```
```{r}
word_over_time_year("avocado") %>% 
  inner_join(avocado_yearly, by = c("year" = "year")) %>% 
  mutate(reddit_index = posts_per_thousand / 3.021148,
         google_index = yearly_google_index / 31.9167) %>%
  select(year, reddit_index, google_index) %>% 
  gather(key = "type", value = "index", 2:3) %>%   # have to reshape data to plot them together on one chart
  arrange(year) %>% 
  ggplot(aes(x = year, y = index, group = type)) +
  geom_col(aes(fill = type)) +
  scale_x_continuous(breaks = c(2010:2019)) +
  theme_minimal() +
  theme(legend.position = "none") +
  facet_wrap(~type, scales = "free", ncol = 1) +
  labs(x = "", y = "index", title = "Interest in Avocados on Google and Reddit's Nutrition Forum",
       caption = "Based on Google Trends data and mentions of Avocado on reddit.com/r/nutrition")
```







### Nutrients
Here, combining sugar, salt, fat, and carbs

```{r}
sugar <- word_over_time_year("sugar") %>% 
  mutate(nutrient = "sugar")

salt <- word_over_time_year("salt") %>% 
  rbind(word_over_time_year("sodium")) %>%
  group_by(year) %>% 
  summarise(n = sum(n), yearly_posts = mean(yearly_posts), posts_per_thousand = sum(posts_per_thousand)) %>% 
  mutate(nutrient = "salt")

fat <- word_over_time_year("fat") %>% 
  mutate(nutrient = "fat")

protein <- word_over_time_year("protein") %>% 
  mutate(nutrient = "protein")

carbs <- word_over_time_year("carbs") %>% 
  rbind(word_over_time_year("carbohydrates")) %>%
  group_by(year) %>% 
  summarise(n = sum(n), yearly_posts = mean(yearly_posts), posts_per_thousand = sum(posts_per_thousand)) %>% 
  mutate(nutrient = "carbs")

fiber <- word_over_time_year("fiber") %>% 
  mutate(nutrient = "fiber")

nutrient_df <- rbind(sugar, salt, fat, protein, carbs, fiber)
```

```{r}
yr_2015_labels <- nutrient_df %>% filter(year == 2015)

nutrient_df %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand, group = nutrient)) +
  geom_line(aes(color = nutrient), size = 1) +
  geom_text_repel(data = nutrient_df %>% filter(year == 2019 |
                                                   year == 2011), aes(label = nutrient)) +
  scale_x_continuous(breaks = c(2010:2019)) +
  theme_fivethirtyeight()+
  theme(legend.position = "none") +
  labs(y = "Mentions per Thousand Posts", title = "The Most Commonly Mentioned Nutrients \non Reddit's Nutrition Forum")
```

```{r}
nutrient_df %>% 
  filter(year > 2010) %>% 
  ggplot(aes(x = year, y = posts_per_thousand, group = nutrient)) +
  geom_col(aes(fill = nutrient), position = "dodge") +
  geom_text(aes(label = nutrient))
```



```{r}
word_over_time_year("sugar") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019)) +  theme_minimal() +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Greek Yogurt Mentions on Reddit's Nutrition Forum")
```
# gut health

```{r}
word_over_time_year("gut") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019)) +
  theme_minimal() +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Gut Health' on Reddit's Nutrition Forum")
```

```{r}
word_over_time_year("amino") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("potassium") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("matcha") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019))
```



```{r}
bigram_year("bone broth") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("turmeric") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("kombucha") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("vinegar") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```
Possible leading indicator to google trends

```{r}
word_over_time_year("fat") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("carbs") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```
Interesting

# Keto
```{r}
word_over_time_year("keto") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019)) +
  theme_minimal() +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Keto' on Reddit's Nutrition Forum")
```
Interesting to compare to broader market /google trends --> moving mass market

```{r}
bigram_year("chia seeds") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```


```{r}
bigram_year("gut health") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019)) +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Gut Health' per Thousand Posts on Reddit's Nutrition Forum") +
  theme_minimal()
```


# kale

```{r}
word_over_time_year("kale") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019)) +
  theme_minimal() +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Kale' on Reddit's Nutrition Forum")
```



```{r}
word_over_time_year("fiber") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("spinach") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```


```{r}
word_over_time_year("quinoa") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```
```{r}
word_over_time_year("cereal") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

Amino acids
```{r}
word_over_time_year("amino") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```


```{r}
word_over_time_year("oatmeal") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```
kalita wave
```{r}
bigram_year("almond milk") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```
What's a steam wand
```{r}
bigram_year("gluten free") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

Buy buy buy!
```{r}
bigram_year("almond butter") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
bigram_year("protein shake") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
bigram_year("grass fed") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
bigram_year("intermittent fasting") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col(fill = "navy") +
  scale_x_continuous(breaks = c(2010:2019)) +
  theme_minimal() +
  labs(x = "", y = "Mentions per Thousand Posts", title = "Mentions of 'Intermittent Fasting' on Reddit's Nutrition Forum")
```

```{r}
bigram_year("coconut oil") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
word_over_time_year("butter") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```

```{r}
bigram_year("bulletproof coffee") %>% 
  ggplot(aes(x = year, y = posts_per_thousand)) +
  geom_col() +
  scale_x_continuous(breaks = c(2010:2019))
```


